Learning Libraries of Subroutines for Neurally--Guided Bayesian Program Learning

### 2018-05-17 nips_2018.tex
table improvements

  \end{tabular}
  \\\bottomrule 
\end{tabular}}\\\\
\caption{Top: Example tasks from each domain, each followed by the programs \system discovers for them. Bottom: Subset of learned DSL. Notice that learned DSL primitives can call each other.}\label{initialExampleDSL}
\end{table}

@@

\begin{table}[b]
\centering  \begin{tabular}{ll}
    \toprule
    Example programs in frontiers&Proposed $\lambda$-expression\\\midrule
    \begin{tabular}{l}
      \code{($\lambda$ (a b) (foldr b (cons "," a)}\\
      \phantom{\code{($\lambda$ }}\code{($\lambda$ (x z) (cons x z))))}\\
      \code{($\lambda$ (a b) (foldr a b }\\
      \phantom{\code{($\lambda$ }}\code{($\lambda$ (x z) (cons x z))))}
    \end{tabular}&
    \begin{tabular}{l}
      \code{(foldr a b ($\lambda$ (x z) }\\
      \phantom{\code{(foldr a b }}\code{(cons x z)))}
    \end{tabular}\\\midrule
    \begin{tabular}{l}
      \code{($\lambda$ (s) (map ($\lambda$ (x)}\\
      \hspace{0.4cm}\code{ (if (= x '.') '-' x))) s)}\\
      \code{($\lambda$ (s) (map ($\lambda$ (x) }\\
      \hspace{0.4cm}\code{ (if (= x '-') ',' x))) s)}\\
      \end{tabular}&
    \begin{tabular}{l}      \code{($\lambda$ (s) (map ($\lambda$ (x)}\\\hspace{0.2cm}\code{   (if (= x '-') ',' x))) s)}
      \end{tabular}
\\\bottomrule
  \end{tabular}
  \caption{The DSL induction algorithm proposes fragments of programs to add to the DSL.
    These fragments are taken from programs in the frontiers (left column). Here, the proposed subexpression (top) appends two lists or (bottom) performs character substitutions.} 
  \label{fragmentExample}
\end{table}

@@

We automatically generated 109 text editing tasks with 4 input/output examples each
%(Fig.~\ref{exampleTextProblem}).
At first, \system cannot find any correct programs for most of the tasks.
After three iterations, it assembles a DSL (Fig.~\ref{firstPageFigure} \& center of Fig.~\ref{initialExampleDSL}) that lets it rapidly explore the space of programs and find solutions to
all of the tasks. The learned DSL contains \textbf{X} new functions, listed in the supplement.

>>>>

  \end{tabular}
  \\\bottomrule\\
\end{tabular}}
\caption{Top: Example tasks from each domain, each followed by the programs \system discovers for them. Bottom: Subset of learned DSL. Notice that learned DSL primitives can call each other.}\label{initialExampleDSL}
\end{table}

@@

\begin{table}[b]
\centering  \begin{tabular}{ll}
    \toprule
    Example programs in frontiers&Proposed $\lambda$-expression\\\midrule
    \begin{tabular}{l}
      \code{($\lambda$ (a b) (foldr b (cons "," a)}\\
      \phantom{\code{($\lambda$ }}\code{($\lambda$ (x z) (cons x z))))}\\
      \code{($\lambda$ (a b) (foldr a b }\\
      \phantom{\code{($\lambda$ }}\code{($\lambda$ (x z) (cons x z))))}
    \end{tabular}&
    \begin{tabular}{l}
      \code{(foldr a b ($\lambda$ (x z) }\\
      \phantom{\code{(foldr a b }}\code{(cons x z)))}
    \end{tabular}\\\midrule
    \begin{tabular}{l}
      \code{($\lambda$ (s) (map ($\lambda$ (x)}\\
      \hspace{0.4cm}\code{ (if (= x '.') '-' x))) s)}\\
      \code{($\lambda$ (s) (map ($\lambda$ (x) }\\
      \hspace{0.4cm}\code{ (if (= x '-') ',' x))) s)}\\
      \end{tabular}&
    \begin{tabular}{l}      \code{($\lambda$ (s) (map ($\lambda$ (x)}\\\hspace{0.2cm}\code{   (if (= x '-') ',' x))) s)}
      \end{tabular}
\\\bottomrule\\
  \end{tabular}
  \caption{The DSL induction algorithm proposes fragments of programs to add to the DSL.
    These fragments are taken from programs in the frontiers (left column). Here, the proposed subexpression (top) appends two lists or (bottom) performs character substitutions.} 
  \label{fragmentExample}
\end{table}

@@

We automatically generated 109 text editing tasks with 4 input/output examples each
%(Fig.~\ref{exampleTextProblem}).
At first, \system cannot find any correct programs for most of the tasks.
After three iterations, it assembles a DSL (Fig.~\ref{firstPageFigure} \& center of Tbl.~\ref{initialExampleDSL}) that lets it rapidly explore the space of programs and find solutions to
all of the tasks. The learned DSL contains \textbf{X} new functions, listed in the supplement.
